Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-18 p2/ordering.tex
Text review

\begin{mylem}\mlabel{simple_distant_pairs}
For any simple sequence $\wrksx{S}$,
if $\cxynv\cc\czwmv$ is a subsequence of $S$ and $n=\parent(m)$ or $\parent(n)=m$,
then $\cxynv\cc\czwmv$ is either a construction or a destruction pair.
\end{mylem}

@@

\begin{proof}
% BACK_TO_FS
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
We assume $\wrks{S}$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
but $S$ contains commands on a node and its parent that do not form a construction or destruction pair.
Select two such commands, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2. \]
As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.

If $n=\parent(m)$, then 
we know $(S_0\cc\cxynv\cc S_1)\FS(n) = y$, and as $[z]\neq[w]$, either
$[(S_0\cc\cxynv\cc S_1)\FS(m)]=[z]\neq[\empt]$,
or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\FS(m)]=[w]\neq[\empt]$.
Therefore $y$ must be $\vald$, as otherwise the tree property would be violated
when applying $\czwmv$,
and $[x]\neq[\vald]$ as $\cxynv$ is not an assertion command.
As $[S_0\FS(n)]=[x]\neq[\vald]$, we know
$S_0\FS(m)=\empt$ as otherwise the tree property would be violated.
Therefore $[S_0\FS(m)]=[z]=[\empt]$, which, combined with $y=\vald$
means that $\cxynv\cc\czwmv$ is a construction pair, which is a contradiction.

If $\parent(n)=m$, then 
as $(S_0\cc\cxynv\cc S_1)\FS(n) = y$, and either
$[(S_0\cc\cxynv\cc S_1)\FS(m)]=[z]\neq[\vald]$
or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\FS(m)]=[w]\neq[\vald]$,
$y$ must be $\empt$, and $[x]\neq[\empt]$.
As $[S_0\FS(n)]=[x]\neq[\empt]$, we know $S_0\FS(m)=\vald$.
Therefore $[S_0\FS(m)]=[z]=[\vald]$, which, combined with $y=\empt$
means that $\cxynv\cc\czwmv$ is a destruction pair, which is a contradiction.
\end{proof}

\begin{mycor}\mlabel{order_is_only_possible}
For any simple sequence $\wrksx{S}$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
We use an inverse proof and assume $\wrksx{S'}$.
If $S'\not\in\orderset{S}$ then by \cref{def_orderrel,def_orderset}
it contains two commands on a node $n$ and its parent
that, as a subsequence,
cannot form a construction or destruction pair.
However, this contradicts \cref{simple_distant_pairs}
which means that no such subsequence exists.
\end{proof}

\begin{mylem}\mlabel{connected_changes}
Given a set of commands that
does not contain assertion commands,
and which can be applied to a filesystem in some order without breaking it,
and which contains commands on $n$ and $\nn$ where $\nn\descendant n$,
then the set must also contain a command
on each node between $n$ and $\nn$.
\end{mylem}
\begin{proof}
% If something changes, everything changes up to the leaves.
Without loss of generality, we can assume that $\nn\neq\parent(n)$.
We prove that under the given conditions, the set must contain a command on $\parent(n)$.
Then, by reapplying this result, we know that the set must contain commands on every
ancestor of $n$ up to $\nn$.

>>>>

\begin{mylem}\mlabel{simple_distant_pairs}
For any simple sequence $\wrksx{S}$ and its subsequence $\cxynv\cc\allowbreak\czwmv$,
if $n=\parent(m)$, then the subsequence is a construction pair;
and if $\parent(n)=m$, then the subsequence is a destruction pair.
\end{mylem}

@@

\begin{proof}
% BACK_TO_FS
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
By assumption $\wrks{S}$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$.
Select two commands on a node and its parent, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2, \]
where any of the three parts can be empty.
As $S$ is simple, there are no commands on $n$ or $m$ in $S_0$, $S_1$, or $S_2$,
and therefore $(S_0\cc\cxynv\cc S_1)\aFS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\aFS(m)] = [S_0\aFS(m)]$,
and so $[z]$ must be $[S_0\aFS(m)]$.

If $n=\parent(m)$, then 
we know $(S_0\cc\cxynv\cc S_1)\aFS(n) = y$, and as $[z]\neq[w]$, either
$[(S_0\cc\cxynv\cc S_1)\allowbreak\aFS(m)]=[z]\neq[\empt]$,
or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\allowbreak\aFS(m)]=[w]\neq[\empt]$.
Therefore $y$ must be $\vald$, as otherwise the tree property would be violated
when applying $\czwmv$,
and $[x]\neq[\vald]$ as $\cxynv$ is not an assertion command.
As $[S_0\aFS(n)]=[x]\neq[\vald]$, we know
$S_0\aFS(m)=\empt$ as otherwise the tree property would be violated.
Therefore $[S_0\aFS(m)]=[z]=[\empt]$, which, combined with $y=\vald$
means that $\cxynv\cc\czwmv$ is a construction pair.

If $\parent(n)=m$, then 
as $(S_0\cc\cxynv\cc S_1)\aFS(n) = y$, and either
$[(S_0\cc\cxynv\cc S_1)\allowbreak\aFS(m)]=[z]\neq[\vald]$
or $[(S_0\cc\cxynv\cc S_1\cc\czwmv)\allowbreak\aFS(m)]=[w]\neq[\vald]$,
$y$ must be $\empt$, and $[x]\neq[\empt]$.
As $[S_0\aFS(n)]=[x]\neq[\empt]$, we know $S_0\aFS(m)=\vald$.
Therefore $[S_0\aFS(m)]=[z]=[\vald]$, which, combined with $y=\empt$
means that $\cxynv\cc\czwmv$ is a destruction pair.
\end{proof}

\begin{mycor}\mlabel{order_is_only_possible}
For any simple sequence $\wrksx{S}$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
If $S'\not\in\orderset{S}$ then by \cref{def_orderrel,def_orderset}
$S'$ contains two commands on a node $n$ and its parent
that, as a subsequence,
form a construction or destruction pair in the wrong order.
\Cref{simple_distant_pairs} implies that no such subsequence exists
if $\wrksx{S'}$, and therefore $S'\equiv\cbrk$.
\end{proof}

\begin{mylem}\mlabel{connected_changes}
Given a set of commands that
does not contain assertion commands,
and which can be applied to a filesystem in some order without breaking it,
and which contains commands on $\nn$ and $n$ where $\nn\descendant n$,
then the set must also contain a command
on each node between $\nn$ and $n$.
\end{mylem}
\begin{proof}
% If something changes, everything changes up to the leaves.
Without loss of generality, we can assume that $\nn\neq\parent(n)$.
We prove that under the given conditions, the set must contain a command on $\parent(n)$.
Then, by reapplying this result, we know that the set must contain commands on every
ancestor of $n$ up to $\nn$.
